
\documentclass[11pt]{article}

% ------------------------------------------------
% Modern packages
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{array}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage[sfdefault,light]{roboto}
\usepackage[T1]{fontenc}

% ------------------------------------------------
% Colors
\definecolor{accent}{HTML}{1E3A5F}
\definecolor{subtext}{HTML}{4A5568}
\definecolor{rulecolor}{HTML}{CBD5E0}

% ------------------------------------------------
% Section formatting with underline
\newcommand{\sectionrule}{\textcolor{rulecolor}{\rule{\linewidth}{0.8pt}}}
\titleformat{\section}
  {\large\bfseries\color{accent}}
  {}
  {0pt}
  {\MakeUppercase}
  [\vspace{-6pt}\sectionrule]
\titlespacing{\section}{0pt}{14pt}{8pt}

% ------------------------------------------------
% Formatting
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=1.2em, itemsep=4pt, topsep=4pt, parsep=0pt}
\renewcommand{\labelitemi}{\textcolor{accent}{\faAngleRight}}

% ------------------------------------------------
% Custom commands
\newcommand{\jobtitle}[4]{%
  \textbf{\large #1} \hfill \textcolor{subtext}{#2}\\[-2pt]
  \textit{\textcolor{subtext}{#3, #4}}%
}

% ------------------------------------------------
\begin{document}

% Header
\begin{center}
    {\Huge\bfseries\color{accent} Yen-Chih Liao}\\[10pt]
    \textcolor{subtext}{%
        \faEnvelope\hspace{4pt}\href{mailto:yen.yenchih.liao@gmail.com}{yen.yenchih.liao@gmail.com}
        \hspace{12pt}|\hspace{12pt}
        \faPhone*\hspace{4pt}(+886) 972-190-248
        \hspace{12pt}|\hspace{12pt}
        \faMapMarker*\hspace{4pt}Wuri Dist, Taichung City 414
    }
\end{center}

\vspace{4pt}

% ------------------------------------------------
\section*{Summary}
Seasoned R\&D Engineer with over four years of software-industry experience across cooperative software development, product research, and implementation. Proficient with Linux-based workflows; skilled in tracing, analyzing, and presenting open-source projects. Strong background in blockchain/Web3 engineering and backend automation. B.S. and M.S. in Computer Science (National Taiwan University). Seeking to contribute to a forward-thinking organization.

% ------------------------------------------------
\section*{Work Experience}

\jobtitle{Web3 Engineer}{Mar 2024 -- Dec 2025}{XY Finance (Web3 team)}{Taipei, Taiwan}
\begin{itemize}
    \item \textbf{Smart Contract Testing \& Auditing:} Authored comprehensive unit tests for Ethereum smart contracts using Foundry; shrunk contract size by 20\% and reduced gas cost by 5\%; increased test coverage by 50\%+.
    \item \textbf{Technical Support \& Reliability:} Diagnosed and resolved rebuild errors in user environments using Foundry toolchain; proposed smart contract dryrun method that speeds up error detection by at least 20x.
    \item \textbf{Seamless Upgrades \& Security:} Orchestrated contract upgrades to align with regulatory and business requirements; coordinated APIs, backend, and database changes achieving continuous availability; reduced later engineering effort by 7x and downtime by 10x.
    \item \textbf{Third-Party Integration:} Successfully integrated product with third-party smart contracts; 88.75\% of users of the same transaction type now benefit from enhanced functionality.
    \item \textbf{Multi-Chain Support:} Broadened product support to L1 (Berachain), L2 (Scroll), and zk-sync L2 (Abstract) networks; introduced 2.1\% traffic and expanded user access across multiple ecosystems.
    \item \textbf{EIP-7702 Frontend Service:} Built a modular wallet system in React/TypeScript supporting EIP-7702 authorization workflows, smart account creation, and multi-wallet compatibility (MetaMask, local keys) with ZeroDev integration.
\end{itemize}

\vspace{8pt}

\jobtitle{R\&D Software Engineer}{Nov 2021 -- Jul 2023}{Taisys (GameFi development team)}{Taipei, Taiwan}
\begin{itemize}
    \item \textbf{Full-Stack Web3 Development:} Launched Solidity contracts with Hardhat; built demo DApps with React; customized and deployed open-source stacks (Omni/TokenBridge, ProjectOpenSea/seadrop, Gnosis/MultiSigWallet); built automated data pipelines on GKE with real-time notifications.
\end{itemize}

\vspace{8pt}

\jobtitle{Contractor (R\&D)}{Apr 2019 -- May 2020}{HTC DeepQ (ML/Healthcare division)}{New Taipei, Taiwan}
\begin{itemize}
    \item Implemented a prototype of \textit{MedRec} (Stanford academy paper) on a private blockchain in a team of five.
\end{itemize}

% ------------------------------------------------
\section*{Skills}

\begin{tabular}{@{} >{\bfseries\color{accent}}l @{\hspace{12pt}} p{13.5cm} @{}}
Programming & Solidity, Python, Go, C++, JavaScript, TypeScript, Shell Script \\[4pt]
Backend & GraphQL, REST APIs, Node.js, MongoDB, Redis \\[4pt]
Web3 Standards & Token Standards, ERC712, ERC4337, ERC4626, ERC7702, ERC7579, Ownable, AccessControl, CREATE2, CREATE3, Upgradeable, Permit, Permit2 \\[4pt]
Cloud & Google Cloud Platform (Cloud SQL, IAM, Secret Manager, GKE, Pub/Sub) \\[4pt]
DevOps & Git, CircleCI pipelines, Docker, Kubernetes \\[4pt]
Frontend & React, Vue.js, Quasar Framework, Next.js
\end{tabular}

% ------------------------------------------------
\section*{Education}

\textbf{\large National Taiwan University} \hfill \textcolor{subtext}{Taipei, Taiwan}

\vspace{6pt}

\textbf{M.S., Networking and Multimedia} \hfill \textcolor{subtext}{Sep 2018 -- Jan 2021}
\begin{itemize}
    \item Research focus: blockchain consensus algorithms for consortium chains.
    \item Publication: \textit{View-base Federated Byzantine Agreement System for Environmental Blockchain} (BRAINS, Jul 2021).
\end{itemize}

\textbf{B.S., Computer Science and Information Engineering} \hfill \textcolor{subtext}{Sep 2014 -- Jun 2018}
\begin{itemize}
    \item Publications: \textit{Applying Blockchain to an Automated Clearinghouse System} (TANET, Oct 2017); \textit{Governance on the Drug Supply Chain via Gcoin Blockchain} (IJERPH, May 2018).
\end{itemize}

% ------------------------------------------------
\section*{Languages}

\faLanguage\hspace{6pt}Mandarin \textcolor{subtext}{(native)}
\hspace{16pt}|\hspace{16pt}
English \textcolor{subtext}{(fluent)}
\hspace{16pt}|\hspace{16pt}
Japanese \textcolor{subtext}{(intermediate; JLPT N2)}

\end{document}
